---
title: "bootstrapping"
author: "Hana Akbarnejad"
date: "11/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}

n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source)
```
In the plot on right we have non-constant variance (different variability in the start and ending of the line and data scattering!)

Fit two models:
```{r}

sim_df_const %>% 
  lm(y ~x, data = .) %>% 
  broom::tidy()

sim_df_nonconst %>% 
  lm(y ~x, data = .) %>% 
  broom::tidy()
```
This is wrong! variability should be higher than this in nonconstant! Can we do some bootsrapping to fix this result?! (happens because R has some assumptions which are not always true)

# Boostrapping code:
write a function to draw bootsrap sample baed on the df:
```{r}

boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```
visualizing:
```{r}

boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

Now we want to analyze many bootsrap samples instead of one!
```{r}

boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

Do some kind of analysis:
```{r}

bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y~x, data = .x)),
    results = map (models, broom::tidy)
  ) %>% 
  select (- strap_sample, -models) %>% 
  unnest(results)
```

summarize results:
```{r}

bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```
These results are different from what we got previousely from nonconstant sample!

Trying 'modelr' package: (doesnt require sample fraction and stuff!)
how to generate bootsrap sample is the only thing which is different from bootsrap function. the rest of the process is exactly the same.
```{r}

boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000)
```

## what if your assumptions aren't wrong?
bootsrap will give us the same result!
```{r}

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

# An example of when things don't work the way we expect them to:
```{r}

data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```


```{r}

nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```

the relationship between stars and price doesnt work how we expect because of the extreme outliers we have. So we need a more realistics approach to see the distribution of slope.

```{r}

airbnb_results = nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) 

# make a plot of stars distribution:
airbnb_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()    # we can see that the plot is skewed!
```

we can solve this with help of bootsrapping!